\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}

\title{Development Plan\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
2025-09-22 & All & Initial draft of development plan.\\
2025-11-18 & Prerna & Address TA feedback on deliverable\\
\bottomrule
\end{tabularx}
\end{table}

\newpage{}

\noindent This report outlines the key elements of our project’s development plan. It covers confidentiality, intellectual property, and licensing, followed by our team’s meeting and communication plans. Roles and responsibilities are defined, along with the Git workflow, project scheduling, and proof of concept demonstration plan. The report also details the technologies and coding standards to be used, and concludes with a reflection and a team charter that set expectations for collaboration and accountability.

\section{Confidential Information?}

This project does not involve the use or disclosure of confidential information 
from any industry partner. All requirements, specifications, and implementation 
details have been developed by the student team. As there is no industry-provided proprietary data 
or trade secrets involved, no Non-Disclosure Agreement (NDA) is required. 

\section{IP to Protect}

All intellectual property (IP) generated as part of this project is owned by the 
student team, in accordance with McMaster University’s policies on ownership of 
student work. Since the project is not sponsored by an external industry partner, 
no Intellectual Property Guide Acknowledgement form is required. To enable the 
intended use of the system, the student team will grant the McMaster Engineering 
Society a non-exclusive license to operate and maintain the software for its 
events and activities. Ownership of the underlying source code remains with the 
student developers. 

\section{Copyright License}

All software developed by the student team is protected under copyright law. 
To clarify permitted use, the team has adopted the MIT License, which is included 
in the project repository
\href{https://github.com/4G06-Streamliners/MacSync/blob/main/LICENSE}{here}. 
This license allows reuse and modification of the code, provided that the 
original copyright notice and license terms are preserved. This ensures proper 
attribution to the development team.

\section{Team Meeting Plan}
The team will meet twice a week. Once online on Monday, from 9:30pm to 10:30pm, to discuss details on work to complete during the week. The second time will be from 5:00pm to 6:30pm to discuss progress, roadblocks, or any issues where assistance is required. This meeting will be online on the weeks there are no in-person progress check-ins and in-person otherwise. \vspace{1em}

The team will meet with the industry advisor online every week on Wednesday during the 4G06 tutorial time from 4:30pm to 5:00pm. This meeting will be to discuss project updates, clear up confusion, and ask for help if needed. \vspace{1em}

Before all meetings, an agenda will be provided. The agenda will cover the main discussion points to guide the conversation in meetings. All meetings will be structured with project updates provided by all team members first, then an update on any roadblocks or issues that need to be dealt with. The end of the meeting will focus on developing a plan for next steps, assigning tasks to each member, and defining an agenda for the next meeting. At the end of the meeting, a record of the meeting minutes will be provided by the chair of the meeting to keep the team accountable for their tasks.





\section{Team Communication Plan}

\begin{flushleft}
\textbf{Main Objectives:} The main objective of the team communication plan is to ensure the team is updated on the tasks they have to complete, the current project progress and the deadlines for completing their tasks. This is to ensure all members are accountable for the progress of the project.\vspace{1em}

\textbf{Communication Platform:} The team's main form of communication will be through Discord for quick updates, project reminders, discussions on division of labour for milestones and getting help for issues faced.\vspace{1em}

\textbf{Response Times:} Maximum 12 hours response time for any form of communication from accepting github issue assignments to message responses on Discord.\vspace{1em}

\textbf{GitHub Issue Tracking:}
\begin{itemize}
    \item Creation of Issues: Issues will be created for every project task, defect or feature and will be linked to the Kanban board.
    \item Issue Assignment: Issues will be assigned to team members based on interest and group consensus. 
    \item Issue Updates: Issue progress will need to be updated in the Kanban board by dragging into “In Progress” state or “Review” state.
    \item Issue Reviews and Closure: Issues will be reviewed by the team to ensure quality standards are met and will then be merged and closed after consensus is reached.
\end{itemize}

\textbf{Conflict Resolution:} Disagreements on responsibilities, division of tasks or ideas escalated to the entirety of the team for a vote to decide on next steps. Final escalation to project supervisor if no consensus reached.

\end{flushleft}


\section{Team Member Roles}

\paragraph{Farhan — Technical Lead \& Research Lead}
\begin{itemize}
    \item Oversees the high-level technical direction for the features assigned to our team (payments, sign-ups, RBAC).
    \item Conducts research on Stripe integration, authentication, and architectural patterns needed for our modules.
    \item Guides team decisions that involve deeper backend complexity, and supports others during technical design reviews.
    \item Coordinates with other teams (A and C) to ensure compatibility of API contracts and shared architecture.
\end{itemize}

\paragraph{Ali — Project Coordinator \& Backend Developer}
\begin{itemize}
    \item Manages project milestones, deadlines, meeting schedules, and documentation updates.
    \item Responsible for backend development tasks related to event creation flows, capacity management, and RBAC endpoints.
    \item Ensures cross-team synchronization on API specifications and helps maintain the shared Postgres/Drizzle schemas.
    \item Maintains clarity between our team’s features and features owned by other teams.
\end{itemize}

\paragraph{Abyan — Frontend Lead \& Documentation Reviewer}
\begin{itemize}
    \item Leads UI development for the attendee and organizer interfaces related to the features our team owns.
    \item Designs React component structures for registration flows, dashboards, and check-in pages.
    \item Conducts final reviews for deliverables to ensure consistent tone, formatting, clarity, and quality.
    \item Works with Ali and Farhan to ensure frontend and backend contract alignment.
\end{itemize}

\paragraph{Prerna — Meeting Chair, Requirements Lead \& Testing Coordinator}
\begin{itemize}
    \item Documents stakeholder needs, requirements, and edge cases within our team’s scope.
    \item Maintains high-quality meeting minutes and outlines weekly priorities.
    \item Coordinates testing plans (unit + integration) for the modules our team owns.
    \item Ensures alignment with user needs by validating that features match problem statement expectations.
\end{itemize}

\paragraph{Mahad — DevOps \& Troubleshooting Lead}
\begin{itemize}
    \item Responsible for GitHub Actions pipelines, CI setup, linting/formatting configuration, and deployment scripts.
    \item Troubleshoots cross-team issues involving repositories, merging conflicts, environment configuration, and Docker.
    \item Supports backend debugging and helps resolve environment-level blockers.
\end{itemize}


\noindent Roles are subject to change based on evolving project needs and further assessment on each team members strengths.




\section{Workflow Plan}

\subsection{Git Usage}
\begin{itemize}
	\item Github will be used as the primary version control system (VCS).
    \item All commits must be made to a non-master branch and submitted via a pull request before they can be merged.
    \item Branching Strategy: \begin{itemize}
    \item Main branch: Stable production-ready code waiting for a release.
    \item Documentation branches: Used to maintain and update project documentation and requirements.
        \begin{itemize}
            \item Notation: \texttt{docs/SL-<Issue\#>}
        \end{itemize}

    \item Development branch: Integration branch where all new features and bug fixes are merged. This branch will contain the latest features with the most up-to-date code. 
        \begin{itemize}
            \item Notation: \texttt{dev}
        \end{itemize}

    \item Feature branches: Used to develop and test new features before merging into the development branch. 
        \begin{itemize}
            \item Notation: \texttt{feature/SL-<Issue\#>}
        \end{itemize}

    \item Bugfix branches: Used to fix defects.
        \begin{itemize}
            \item Notation: \texttt{bugfix/SL-<Issue\#>}
        \end{itemize}
\end{itemize}
\end{itemize}

\subsection{Issues and Project Management}
\begin{itemize}
    \item Github issues will serve as the primary issue/ticket system
    \item All subsections of each document/report will have its own issue
    \item All new tasks and/or features will have its own issue
    \item Issues will be classified to using labels (e.g., \texttt{documentation}, \texttt{feature}, \texttt{bug}).
    \item Github's Kanban board will be used to monitor progress
\end{itemize}

\subsection{CI/CD Usage}
\begin{itemize}
    \item A CI/CD pipeline will be implemented using Github Actions.
    \item Continuous Integration \textbf{(CI)}:
    \begin{itemize}
        \item Automatically build the project and run tests on every pull request.
    \end{itemize}
    \item Continuous Deployment \textbf{(CD)}:
    \begin{itemize}
        \item Deploy staging builds after merging to development branch.
        \item Deploy production builds after merging to main branch.
    \end{itemize}
\end{itemize}

\section{Project Decomposition and Scheduling}

\begin{itemize}
  \item GitHub projects will act as the primary to-do list and milestone tracker.
  \item Tasks will be broken down into various issues that will be assigned to team members during sprint planning.
  \item Issues will be linked to a Kanban board that will be broken up into: \texttt{Ready} $\rightarrow$ \texttt{In Progress} $\rightarrow$ \texttt{In Review} $\rightarrow$ \texttt{Done}.
  \item Issues will be categorized under GitHub Milestones/Deliverables. Milestones will have deadlines that will aid in prioritizing issues.
  \item Milestone deadlines and deliverables provided in the course Google calendar will be the primary source for planning sprints. 
  \item The team will meet at the beginning of each week to assign new issues and monitor progress.
  \item GitHub Project link:
  \url{https://github.com/orgs/4G06-Streamliners/projects/2}
\end{itemize}

\section{Proof of Concept Demonstration Plan}

\subsection*{The Primary Risks Addressed by the POC are as follows:}

\begin{itemize}
    \item \textbf{Architectural Integration Risk}: The ability to seemlessly integrate frontend, backend, database, and shared APIs and interacting smoothly across teams.
    \item \textbf{Inter-Team Merge Risk}: Conflicting implementations across teams must not break shared components
    \item \textbf{Usability Risk}: End users must be able to use all features intuitively without confusion.
    \item \textbf{Payment Processing Risk}: Stripe configuration, webhooks, and error handling must work reliably.
    \item \textbf{Role-Based Access Risk}: RBAC must enforce correct permissions before more complex features depend on it.
    \item \textbf{Capacity Management Risk}: Bus/table sign-ups must prevent overbooking in a real-time environment.
    .
\end{itemize}

\subsection*{POC Demonstration overcoming these risks will consist of:}

The POC will demonstrate:
\begin{itemize}
    \item A minimal but functional demo showcasing the different architecture layers working cohesively.
    \item A minimal working registration-to-payment workflow.
    \item A functional RBAC setup with two sample roles (attendee and organizer).
    \item A prototype of bus/table sign-ups controlling capacity in the shared database.
    \item A walkthrough showing a general end-user workflow (i.e. registering for events, paying for events, creating events, etc.).

\end{itemize}

\noindent The POC is not a feature-complete product; rather, it is a validation that the
riskiest parts of the architecture can be implemented and merged successfully
across teams. A failed POC signals that core architecture, dependencies, or
integrations need revision before full implementation begins.

\section{Expected Technology}

\subsubsection*{Languages \& Frameworks} 
The team will use \textbf{JavaScript} as the primary language across the stack. 
The web application will be built with \textbf{Next.js (React)}, the mobile application with \textbf{React Native}, 
and the backend will be developed using \textbf{NestJS} (chosen for its opinionated structure atop Express).

\subsubsection*{Database \& ORM} 
The database will be \textbf{PostgreSQL}, self-managed via a Docker container. 
For database access, the team is considering \textbf{Drizzle ORM} as the shared standard across groups.

\subsubsection*{Payments} 
Payments will be handled through \textbf{Stripe}, integrated using official SDKs. 
Processor-specific logic will be isolated within the backend service.

\subsubsection*{Selected Libraries (initial)}
\begin{itemize}
  \item \textbf{Frontend:} a React component library (e.g., Tailwind or Material UI) to accelerate UI development.
  \item \textbf{Backend:} NestJS modules for routing/validation; Stripe SDK for payments; Drizzle ORM for database access.
\end{itemize}

\subsubsection*{Custom Components Expected to Be Implemented} 
Despite the existence of some libraries, the team anticipates implementing core logic to align with project requirements:
\begin{itemize}
  \item \textbf{Feature-Based Access Control (FBAC)} with role templates and per-user overrides.
  \item \textbf{Sign-up capacity/hold logic} (e.g., bus/table/RSVP) to safely manage contention and inventory.
\end{itemize}

\subsubsection*{Dev Workflow \& Tooling}
\begin{itemize}
  \item \textbf{Git} for version control; \textbf{GitHub} for repository management; \textbf{GitHub Projects} for task tracking.
  \item Production hosting will be on \textbf{DigitalOcean} (school-hosted), with Postgres running in Docker.
\end{itemize}

\subsubsection*{Testing, CI/CD, and Performance} 
The team intends to adopt a layered testing strategy:
\begin{itemize}
  \item \textbf{Unit tests} for backend modules (NestJS services/controllers) and React components.
  \item \textbf{Integration tests} to validate backend endpoints against a local Postgres instance.
  \item \textbf{End-to-end (E2E) tests} for critical flows such as checkout, sign-ups, and access control.
\end{itemize}
Continuous Integration will be run through \textbf{GitHub Actions}, with pipelines for linting, type-checking, running automated tests, and validating database migrations.

\section{Coding Standard}

The team will adopt consistent coding standards to ensure readability, maintainability, and effective collaboration. For JavaScript code, the team will follow the \href{https://github.com/airbnb/javascript}{Airbnb JavaScript Style Guide}, which provides well-established conventions for formatting and best practices. Code formatting will be automated with \textbf{Prettier}, and linting will be enforced with \textbf{ESLint} to reduce inconsistencies across contributions.

Naming conventions will remain uniform across the stack:
\begin{itemize}
  \item \texttt{camelCase} for variables and functions
  \item \texttt{PascalCase} for React components and NestJS classes
  \item \texttt{snake\_case} for PostgreSQL tables and column names
\end{itemize}

Beyond style rules, the team will apply \textbf{Clean Code principles} to keep the codebase simple and easy to understand. This means writing small and focused functions, choosing descriptive names, avoiding duplication, and keeping modules cohesive. Comments will be added only where necessary to clarify complex logic, with the preference being self-explanatory code.

For version control, all work will be done in feature branches, with pull requests reviewed before merging into \texttt{staging} or \texttt{main}. Commit messages will follow the imperative style (for example, “Add payment processing logic”) to maintain a clear project history.

\newpage{}

\section*{Appendix --- Reflection}

\begin{enumerate}
    \item Why is it important to create a development plan prior to starting the
    project?

    Creating a development plan helped the team align on goals, expectations, and responsibilities before beginning development. Because this project spans multiple groups, documenting decisions early established a common foundation and reduced the risk of misunderstandings later. It also encouraged us to think ahead about technologies, workflows, and risks, which gave the team more confidence moving into implementation.
    
    \item In your opinion, what are the advantages and disadvantages of using
    CI/CD?

    The advantages of CI/CD include automated testing, faster feedback, and reduced integration issues. It helps ensure that code changes are validated continuously, which improves reliability and makes collaboration smoother. On the other hand, the disadvantages are the upfront setup effort and the need for ongoing maintenance of pipelines. For a student project with limited time, the main challenge is balancing the investment in CI/CD with the need to deliver features quickly.
    
    \item What disagreements did your group have in this deliverable, if any,
    and how did you resolve them?
   
    The team did not have any major disagreements, but there were discussions around which ORM should be used. Some members had experience with Prisma, while others were interested in Drizzle for its modern features and close mapping to SQL. After reviewing the trade-offs together and following up with the mentors for additional guidance, the team decided to move forward with Drizzle as the preferred option. This process allowed the team to weigh different perspectives while still keeping flexibility in case future integration across groups requires adjustments.
\end{enumerate}

\noindent
\textbf{Overall, this deliverable reinforced the importance of careful planning, open communication, and collaborative decision-making.} By documenting our expectations early, reflecting on the role of CI/CD, and carefully weighing options for the technology stack, the team not only produced a development plan but also practiced the skills needed to sustain long-term teamwork. These lessons will continue to shape how we approach challenges in the later stages of the project.

\newpage{}

\section*{Appendix --- Team Charter}

\subsection*{External Goals}
\begin{itemize}
    \item Secure a grade of A+ in 4G06.
    \item Gain real-world experience in areas of project management, teamwork and shipping projects.
    \item Create a strong portfolio project that has a large user base and can be discussed in interviews.  
\end{itemize}


\subsection*{Attendance}

\subsubsection*{Expectations}
\begin{itemize}
    \item All members are expected to attend all scheduled meetings either in-person or online.
    \item All members are expected to be on time for meetings and remain present for the duration of the meeting.
    \item All members are expected to notify the team 24 hours beforehand if they are unable to attend meetings.
\end{itemize}

\subsubsection*{Acceptable Excuse}
Acceptable excuses for missing meetings or deadlines include the following:
\begin{itemize}
    \item Family emergency
    \item Health issues
    \item Medical appointments
\end{itemize}
Unacceptable excuses for missing meetings or deadlines include the following:
\begin{itemize}
    \item Forgetting about meetings
    \item Oversleeping
\end{itemize}

\subsubsection*{In Case of Emergency}
\begin{itemize}
    \item If the emergency affects the members ability to attend a meeting, they must notify the group immediately or as soon as possible after the emergency.
    \item If the emergency affects completion of work, the member must communicate explicitly what work is done and what remains so the team can decide on the division of labour or a plan to catch-up.
\end{itemize}


\subsection*{Accountability and Teamwork}

\subsubsection*{Quality} 
\begin{itemize}
    \item All members must come to meetings prepared with progress updates on their tasks.
    \item Deliverables should be well-organized and reviewed before they are shared with the team.
    \item Contributions in the code repository must follow team standards for readability and documentation.
\end{itemize}

\subsubsection*{Attitude}
\begin{itemize}
    \item All members must listen actively to all other members and avoid passive or dismissive behavior.
    \item All members should respect all ideas and viewpoints without judgment.
    \item All members are encouraged to share their ideas openly.
    \item All members must adopt a simple code of conduct revolving on principles of respect, communication and collaboration.
    \item Conflicts must be resolved respectfully and if unresolved will be escalated to the TA.
\end{itemize}

\subsubsection*{Stay on Track}
\begin{itemize}
    \item Weekly progress check-ins where members discuss what they completed and next steps will be used to keep the team on track. 
    \item GitHub Issues and commits will be used to ensure members contribute as expected.
    
    \item Metrics: \begin{itemize}
        \item An attendance rate of 100\% is expected from all members unless an excuse is deemed valid and acceptable by the team.
        \item Consistent GitHub activity is expected per week with issues in progress or items being committed for review.
        \item On-time delivery of tasks on assigned deadlines.
    \end{itemize}
    \item Rewards: \begin{itemize}
        \item Members who reach targets early or who do well overall will be rewarded with acknowledgments of being strong contributors. \end{itemize}
    \item Consequences: \begin{itemize}
        \item First time incident will be a verbal reminder.
        \item Second time will result in a discussion with the TA.
        \item Third time and more will result in escalation to the course instructor.
    \end{itemize}
\end{itemize}

\subsubsection*{Team Building}
\begin{itemize}
    \item Start meetings with small talk and conversations to get to know each other and maintain team connection.
    \item Doing a group ritual of small activities like board games or lunch to celebrate milestone deliveries.
\end{itemize}

\subsubsection*{Decision Making} 
\begin{itemize}
    \item Initial plan will be to reach consensus when possible.
    \item If consensus cannot be reached, opt for a majority vote.
    \item If disagreements still exist within the team if consensus and majority vote leaves members unsatisfied, involve the TA for handling disagreements.
\end{itemize}


\end{document}