\documentclass[12pt]{article}

\usepackage[round]{natbib}
\usepackage{hyperref}
\hypersetup{colorlinks=true,
    linkcolor=blue,
    citecolor=blue,
    filecolor=blue,
    urlcolor=blue,
    unicode=false}
\urlstyle{same}

\usepackage{enumitem,amssymb}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}%
\hspace{-2.5pt}}
\newcommand{\wontfix}{\rlap{$\square$}{\large\hspace{1pt}\xmark}}

\begin{document}

\title{Development Plan Checklist}
\author{Spencer Smith}
\date{\today}

\maketitle

% Show an item is done by   \item[\done] Frame the problem
% Show an item will not be fixed by   \item[\wontfix] profit

The Development Plan records important decision for the team on the agreed upon
approach for the project.

\begin{itemize}
\item Follows writing checklist (full checklist provided in a separate document)
  \begin{todolist}
<<<<<<< HEAD
  \item [\cmark]\LaTeX{} points
  \item [\cmark]Structure
  \item [\cmark]Spelling, grammar, attention to detail
  \item [\cmark]Avoid low information content phrases
  \item [\cmark]Writing style
  \item [\cmark]Hyperlinks should be done properly (\texttt{\textbackslash ref})
=======
  \item \LaTeX{} points
  \item Structure
  \item Spelling, grammar, attention to detail
  \item Avoid low information content phrases
  \item Writing style
  \item Hyperlinks should be done properly (\texttt{\textbackslash ref})
>>>>>>> boilerplate/main
  \end{todolist}

\item Document
  \begin{todolist}
<<<<<<< HEAD
  \item [\cmark]Follows outline in template repo (minor changes are okay, as long as
  rubric items are covered)
  \item [\cmark]Document makes decisions (not an empty exercise).  Decisions can be changed later.
  \item [\cmark]PoC demo plans are included (they can be changed later if necessary)
  \item [\cmark]Risk used to plan PoC is clearly expressed
=======
  \item Follows outline in template repo (minor changes are okay, as long as
  rubric items are covered)
  \item Document makes decisions (not an empty exercise).  Decisions can be changed later.
  \item PoC demo plans are included (they can be changed later if necessary)
  \item Risk used to plan PoC is clearly expressed
  \item PoC plan is NOT described as a prototype (the PoC should be less
  ambitious and more focused than a prototype)
  \item Mitigation strategies for a ``failed'' PoC are NOT provided.  We can
  discuss how to redefine the scope after the PoC demo.
  \item Team members have been given project-level roles (e.g. meeting chair, team liaison, etc.)
  \item Team members have technical roles (e.g. back-end, front-end, pytorch expert, etc.)
  \item Team roles are assigned with flexibility and overlap.  Too rigid a
  structure is potentially problematic.
>>>>>>> boilerplate/main
  \end{todolist}

\item{Team Charter}
\begin{todolist}
<<<<<<< HEAD
  \item [\cmark]Trigger for a problem is quantified
  \item [\cmark]Consequence of problematic behaviour is expressed
  \item [\cmark]Exercise of planning team charter is done with sincerity
=======
  \item Trigger for a problem is quantified
  \item Consequence of problematic behaviour is expressed
  \item Exercise of planning team charter is done with sincerity
>>>>>>> boilerplate/main
  \end{todolist}

\end{itemize}

\end{document}
